Sell Prevention and Buy Cure: An Exploration of Indirect Conflicts

### 2014-01-31 iced-2013/paper.tex
ICED intro fixes.

While indirect conflict tools have shown potential from studies of developers, some of the same problems continue
to arise throughout most, if not all tools. The most prevalent issue is that of false positives and information
overload, tools eventually being
ignored~\cite{Sarma:2007:TSA, Servant:2010:CPI}. A second primary issue is that of dependency identification and
tracking. Many different dependencies have been proposed and used in indirect conflict tools such as method 
invocation~\cite{Trainer:2005:BGT}, and class signatures~\cite{Sarma:2007:TSA} with varying success, but the 
identification of failure inducing changes, other than those which are already identifiable by other means such
as compilers, and unit tests, to these dependencies still remains an issue. Dependency tracking issues are
also compounded by the scale of many software development projects leading to further information overload.
Lastly, social factors such as Cataldo et al.~\cite{Cataldo:2006:ICR} notion of socio-technical
congruence have been leveraged in indirect conflict tools~\cite{Kwan:2011:ESC, Begel:2010:CDE, Borici:2012:CHA}.
However, issues again of information overload, dependencies (in developer organizational structure), and scalability 
come up.

In order to investigate the root causes of information overload, false positives, and
scalability issues in regards to indirect conflicts, we conducted an empirical study to determine what events occur to
cause indirect conflicts, when they occur, and if conditions exist to provoke more of these events. 
We then set out to understand what mitigation strategies developers currently use as opposed to those created
by academia. Through this exploration, we look to find what can be accomplished moving forward with indirect conflicts
in both research and industry and how we can get over the road block of these information overload related
issues. To accomplish these goals, we ask the following:

>>>>

While indirect conflict tools have shown potential from studies of developers, some of the same problems continue
to arise throughout most, if not all tools. The most prevalent issue is that of false positives and information
overload, tools eventually being
ignored~\cite{Sarma:2007:TSA, Servant:2010:CPI}. A second primary issue is that of dependency identification and
tracking. Many different dependencies have been proposed and used in indirect conflict tools such as method
invocation~\cite{Trainer:2005:BGT}, and class signatures~\cite{Sarma:2007:TSA} with varying success, but the
identification of failure inducing changes, other than those which are already identifiable by other means such
as compilers, and unit tests, to these dependencies still remains an issue.
Lastly, social factors such as Cataldo et al.~\cite{Cataldo:2006:ICR} notion of socio-technical
congruence have been leveraged in indirect conflict tools~\cite{Kwan:2011:ESC, Begel:2010:CDE, Borici:2012:CHA}.
However, issues again of information overload, dependencies (in developer organizational structure), and scalability
come up. All the aforementioned tools have not been able to study their own problems as their evaluations have
been small scale, involving a very limited number of industrial participants or student evaluators.

In order to investigate the root causes of information overload, false positives, and
scalability issues in regards to indirect conflicts, we conducted a large scale an empirical study involving industrial
participants in order to determine: what events occur to
cause indirect conflicts, when they occur, if compounding conditions exist, and what mitigation strategies developers currently
use. Through this large exploration, we look to find what can be accomplished moving forward with indirect conflicts
in both research and industry and how we can get over the road block of these information overload related
issues. To accomplish these goals, we ask the following:
